Title

### 2018-08-19 thesis/paper/paper.tex
Adapted rules in paper for two required terms

Using this pre-processed data the approach is to apply a require-predicate to each statement or qualifier. This is require\([2]\) for statements, connecting the statement ID with a required term \(t\) and require\([4]\) taking the statement ID, property, and value of a qualifier and linking this with the term \(t\).\\

For statements the pattern consists of two rules, both utilising the same conjunction \(c = C_1 \wedge .. \wedge C_m\) with arbitrary atoms \(C_n\) which is used to test if the statement does not fulfil the requirement. Then rule one
\begin{equation*}
\text{require}(S, t) \leftarrow \text{first}(S, I) \wedge c
\end{equation*}
states that the statement requires the condition and
\begin{equation*}
\text{require}(S, t) \leftarrow \text{next}(O, S) \wedge \text{require}(O, t) \wedge c
\end{equation*}
propagates this down the statement chain.

For qualifiers the rules are
\begin{equation*}
\text{require}(S, P, V, t) \leftarrow \text{first}(S, P, V) \wedge c
\end{equation*}
\begin{equation*}
\text{require}(S, P, V, t) \leftarrow \text{next}(O, X, C, S, P, V) \wedge \text{require}(O, X, C, t) \wedge c
\end{equation*}

@@

\subsection{Item requires statement (Q21503247)}
The item requires statement constraint requires the pre-processing of all item statements. Additionally, inequality between all properties of item statements and the required property as well as between all values and the allowed values has to be established. It occurs in two varieties, depending on if allowed values have been specified or not. The required term \(t\) is the  required property. Without separators the conjunction is \(c_1 = \text{tripleEDB}(S, I, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)\).\\

If a set of allowed values \(A\) has been specified, a second set of require-rules have to be introduced with \(c_2 = \text{tripleEDB}(S, I, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)\). Note that the first set of rules is still required, since the preceding statements do not need to have the required property.\\

In both cases violations can be found with
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{tripleEDB}(O, I, P, X) \wedge \text{last}(O, I) \wedge \\
&\text{require}(O, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

\subsection{Value requires statement (Q21510864)}
The value requires statement constraint is syntactically very similar to the previous item requires statement constraint. Instead of requiring a statement on the item of a constrained statement it requires it on the value. The pre-processing changes to extracting all value statements along the constrained statements and ordering them. Inequality need to be computed between all properties and all values on value statements. The conjunctions remain the same and the final violation rule is
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{tripleEDB}(O, V, P, X) \wedge \text{last}(O, V) \wedge \\
&\text{require}(O, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

\subsection{Inverse (Q21510855)}
The inverse constraint is similar to the value requires statement constraint in requiring a statement on a constrained value with a specific property. However, instead of putting no constraint or a list of fixed values on the required statements value it set a relative requirement: the constrained item. The pre-processing and inequalities thus remain the same, but the conjunctions change to 
\begin{equation*}
c_1 = \text{tripleEDB}(S, I, P, V) \wedge \text{unequal}(\text{inversePropertyConstant}, P)
\end{equation*}
\begin{equation*}
\begin{split}
c_2 = &\text{tripleEDB}(O, R, \text{propertyConstant}, X) \wedge \\
&\text{tripleEDB}(S, I, \text{inversePropertyConstant}, V) \wedge \\
&\text{unequal}(R, V)
\end{split}
\end{equation*}

>>>>

Using this pre-processed data the approach is to apply a require-predicate to each statement or qualifier. This is require\([3]\) for statements, connecting the statement ID with the constrained property \(p\) and the required term \(t\) and require\([5]\) taking the statement ID, property, and value of a qualifier and linking this with \(p\) and \(t\).\\

For statements the pattern consists of two rules, both utilising the same conjunction \(c = C_1 \wedge .. \wedge C_m\) with arbitrary atoms \(C_n\) which is used to test if the statement does not fulfil the requirement. Then rule one
\begin{equation*}
\text{require}(S, p, t) \leftarrow \text{first}(S, I) \wedge c
\end{equation*}
states that the statement requires the condition and
\begin{equation*}
\text{require}(S, p, t) \leftarrow \text{next}(O, S) \wedge \text{require}(O, p, t) \wedge c
\end{equation*}
propagates this down the statement chain.

For qualifiers the rules are
\begin{equation*}
\text{require}(S, P, V, p, t) \leftarrow \text{first}(S, P, V) \wedge c
\end{equation*}
\begin{equation*}
\text{require}(S, P, V, p, t) \leftarrow \text{next}(O, X, C, S, P, V) \wedge \text{require}(O, X, C, p, t) \wedge c
\end{equation*}

@@

\subsection{Item requires statement (Q21503247)}
The item requires statement constraint requires the pre-processing of all item statements. Additionally, inequality between all properties of item statements and the required property as well as between all values and the allowed values has to be established. It occurs in two varieties, depending on if allowed values have been specified or not. The required term \(t\) is the  required property. Without separators the conjunction is
\begin{equation*}
\begin{split}
c_1 = &\text{tripleEDB}(O, I, \text{propertyConstant}, X) \wedge \\
&\text{tripleEDB}(S, I, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split}
\end{equation*} \(\)
If a set of allowed values \(A\) has been specified, a second set of require-rules have to be introduced with
\begin{equation*}
\begin{split}
c_2 = &\text{tripleEDB}(O, I, \text{propertyConstant}, X) \wedge \\
&\text{tripleEDB}(S, I, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{equation*}
Note that the first set of rules is still required, since the preceding statements do not need to have the required property. In both cases violations can be found with
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{tripleEDB}(O, I, P, X) \wedge \text{last}(O, I) \wedge \\
&\text{require}(O, \text{propertyConstant}, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

\subsection{Value requires statement (Q21510864)}
The value requires statement constraint is syntactically very similar to the previous item requires statement constraint. Instead of requiring a statement on the item of a constrained statement it requires it on the value. The pre-processing changes to extracting all value statements along the constrained statements and ordering them. Inequality need to be computed between all properties and all values on value statements. The conjunctions remain the same and the final violation rule is
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{tripleEDB}(O, V, P, X) \wedge \text{last}(O, V) \wedge \\
&\text{require}(O, text{propertyConstant}, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

\subsection{Inverse (Q21510855)}
The inverse constraint is similar to the value requires statement constraint in requiring a statement on a constrained value with a specific property. However, instead of putting no constraint or a list of fixed values on the required statements value it set a relative requirement: the constrained item, meaning \(t = R\). The pre-processing and inequalities thus remain the same, but the conjunctions change to 
\begin{equation*}
\begin{split}
c_1 = &\text{tripleEDB}(O, R, \text{propertyConstant}, I) \wedge \\
&\text{tripleEDB}(S, I, P, V) \wedge \\
&\text{unequal}(\text{inversePropertyConstant}, P)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
c_2 = &\text{tripleEDB}(O, R, \text{propertyConstant}, I) \wedge \\
&\text{tripleEDB}(S, I, \text{inversePropertyConstant}, V) \wedge \\
&\text{unequal}(R, V)
\end{split}
\end{equation*}
